Twists of Supersymmetric Gauge Theories

### 2020-01-15 paper.tex
Minor edit
Section headers

\title{Twists of supersymmetric gauge theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

@@

\part{A Catalogue of Twists}

@@

>>>>

\title{Twists of Supersymmetric Gauge Theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

@@

\part{A Catalogue of Twists}
\chris{We actually used this heading in our previous paper, so maybe a different name?}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(8,8)}
